### 2018-05-11 paper/paper.tex
updated figure inventory

\includegraphics[width=.7\paperwidth]{/Users/tonhauser.1/Documents/current-research-topics/NSF-NAI/prop-att-experiments/2evaluative-adjectives/7-corpus-data/graphs/mean-response-by-item-and-adj}

@@

\includegraphics[width=1\textwidth]{/Users/tonhauser.1/Documents/current-research-topics/NSF-NAI/prop-att-experiments/1factive-verbs/Git-variability/results/exp1a/graphs/subject-projai-stupid}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[scale=.7]{/Users/tonhauser.1/Documents/current-research-topics/NSF-NAI/prop-att-experiments/2evaluative-adjectives/content-context-experiment/results/graphs/targetmeans-by-condition-and-adj}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[scale=.6]{/Users/tonhauser.1/Documents/current-research-topics/NSF-NAI/prop-att-experiments/2evaluative-adjectives/6-NAI-positive-EAS/results/graphs/proportion-ai-by-condition-and-adj}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[scale=.9]{/Users/tonhauser.1/Documents/current-research-topics/NSF-NAI/prop-att-experiments/2evaluative-adjectives/content-context-experiment/results/graphs/count-of-participants}

@@

\hspace*{-.5cm}\includegraphics[scale=.8]{/Users/tonhauser.1/Documents/current-research-topics/NSF-NAI/prop-att-experiments/2evaluative-adjectives/acceptability-experiment/results/graphs/histogram} \includegraphics[scale=.8]{/Users/tonhauser.1/Documents/current-research-topics/NSF-NAI/prop-att-experiments/2evaluative-adjectives/acceptability-experiment/results/graphs/acceptability-rating-difference}

>>>>

\includegraphics[width=.7\paperwidth]{../corpus-study/graphs/mean-response-by-item-and-adj}

@@

\includegraphics[width=1\textwidth]{figures/Exp1a-subject-projai-stupid}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[scale=.7]{../exp1/graphs/targetmeans-by-condition-and-adj}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[scale=.6]{../exp2/graphs/proportion-ai-by-condition-and-adj}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[scale=.9]{../exp1/graphs/count-of-participants}

@@

\hspace*{-.5cm}\includegraphics[scale=.8]{../acceptability-rating-study/graphs/histogram} \includegraphics[scale=.8]{../acceptability-rating-study/graphs/acceptability-rating-difference}
